Kaggle Titantic Data Cleaning
======================================

# Introduction

In the package, when the data is imported, it follows the procedure:

1. Get data from csv file

2. Fill data gap

3. Rename columns

4. Add new parameters


## Fill data gap

### Embarked

All `na` values of "Embarked" is mapped to "S"

```{r code = capture.output(dump('clean.data.embarked', ''))}

```

### Fare

For fares less than $0.1, they are mapped into the median.

```{r code = capture.output(dump('clean.data.fare', ''))}

```

### Age

The missing age is filled by median, grouped by sex.

```{r code = capture.output(dump('clean.data.age', ''))}

```

### Survived

The value of "1" and "0" is mapped to "Survive" and "Perish".


```{r code = capture.output(dump('clean.data.survived', ''))}

```


## Add new parameters

### Title

Some uncommon titles are mapped into common ones:

1. "the Countess" and "Ms" -> "Mrs"

2. "Mlle" and "Mme" -> "Miss"

3. Titles other than "Master", "Miss", "Mr" and "Mrs" -> "Noble"

```{r code = capture.output(dump('get.title.from', ''))}

```

### Family size

Familiy size is calculated by adding "SibSp", "Parch" and then incremented by 1.

```{r code = capture.output(dump('get.familySize', ''))}

```

### Children

From the analysis the survival rate of children is high. "IsChild" is mapped if the age is less than 18 and family size is more than 1.

```{r code = capture.output(dump('get.isChild', ''))}

```

### Rich girl

From the analysis the survival rate of a first and second class young woman is high. "IsRichGirl" is mapped if a woman younger than 30 is on first and second class.


```{r code = capture.output(dump('get.isRichGirl', ''))}

```

### Poor and old

From the analysis a third class poor guy is probably passed away. "IsPoorOld" is mapped if age is higher than 40 and he stayed on third class.

```{r code = capture.output(dump('get.isPoorOld', ''))}

```
